Robust Bayesian Analysis of Causal Inference Problems

### 2024-03-21 JASA-template.tex
Make suggestion.
Some fixes.

Let $\pi_j$ denote the prior probability that the $j$-th
predictor is associated with the outcome or the 
treatment. That is, 
\begin{equation}
	\pi_j \coloneqq P\left((\beta_j,\gamma_j)\not=(0,0)\right).
\end{equation}
Then we can define the following hierarchical model for spike and 
slab group LASSO so that,
for $1\le j\le p$,
\begin{align}
	(\beta_j,\gamma_j)^T \mid \pi_{j}, \sigma^2 &\sim 
	\pi_{j}\normal\left( \begin{bmatrix}
		0 \\
		0
	\end{bmatrix}, 
	\tau_1^2\begin{bmatrix}
		\sigma^2 & 0 \\
		0 & 1
	\end{bmatrix}\right)
	+ (1-\pi_{j}) \normal\left(\begin{bmatrix}
		0 \\
		0
	\end{bmatrix}, 
	\tau_0^2\begin{bmatrix}
		\sigma^2 & 0 \\
		0 & 1
	\end{bmatrix}\right)\\
	\beta_T\mid \sigma^2 &\sim \normal\left(0, \sigma^2\right)\\
	\frac{1}{\sigma^2}&\sim \text{Gamma}(a, b)\\
	\pi_{j} &\sim\text{Beta}\left(sq, s(1-q)\right).
\end{align}
In the hierarchical model, we fix sufficiently small $\tau_0$
$(1\gg\tau_0>0)$ so that  $(\beta_j, \gamma_j)$ has its probability mass 
concentrated around zero. Therefore, this represents the spike component of our prior specification. 
For the slab component, we consider $\tau_1$ to be large so that $\tau_1\ge 1$. This allows the prior for $(\beta_j,\gamma_j)$ to be flat beyond the spike component at the origin. 
We illustrate the components of a bivariate spike and slab prior in 
\cref{fig:ssbl} (with fixed $\sigma=1$). We generate the spike component 
with $\tau_0=0.001$ and the slab component with $\tau_1=5$.

@@

For the precision term $1/\sigma^2$, a natural choice of prior is the gamma distribution
as it allows the control of both the location and the scale of the precision.
%%% MT to TB: why not simply say the prior is exponential?
To ensure that the prior is able to represent the data, we consider $b=1$ and 
fix $a$ so that it represents the prior mean of the precision.
%%% MT to TB: "no prior information" seems a bit misleading here? I suggest removing
% In cases where we have no prior information,
We can simply consider a large enough value for $a$
%%% MT to TB: the next phrase is confusing... do you mean to say "with probability ..." (not sure what that is for [0,2a]))
so that the interval
$[0, 2a]$ contains the true value of the precision.
As defined earlier, $\pi_j$ is used as the selection probability
of the $j$-th predictor in either of the models and we use a beta prior to specify 
these selection probabilities where  $q_j$ represents our prior expectation of the selection probability ($\pi_j$) and $s$ acts as 
a concentration parameter.
For the causal effect, we want to use a Gaussian distribution that 
matches the scale of the noise term. Therefore, we consider $\beta_T\sim \normal(0,\sigma^2)$.

>>>>

Let $\pi_j$ denote the prior probability that the $j$-th
predictor is associated with the outcome or the 
treatment. That is, 
\begin{equation}
	\pi_j \coloneqq P\left((\beta_j,\gamma_j)\not=(0,0)\right).
\end{equation}
Then we can define the following hierarchical model for spike and 
slab group LASSO so that,
for $1\le j\le p$,
\begin{align}
	(\beta_j,\gamma_j)^T \mid \pi_{j}, \sigma^2 &\sim 
	\pi_{j}\normal\left( \begin{bmatrix}
		0 \\
		0
	\end{bmatrix}, 
	\tau_1^2\begin{bmatrix}
		\sigma^2 & 0 \\
		0 & 1
	\end{bmatrix}\right)
	+ (1-\pi_{j}) \normal\left(\begin{bmatrix}
		0 \\
		0
	\end{bmatrix}, 
	\tau_0^2\begin{bmatrix}
		\sigma^2 & 0 \\
		0 & 1
	\end{bmatrix}\right)\\
	\beta_T\mid \sigma^2 &\sim \normal\left(0, \sigma^2\right)\\
        \frac{1}{\sigma^2}&\sim \text{Gamma}(a, b)\\
        %%% MT to TB: text referred to q_j so I changed q -> q_j here
	\pi_{j} &\sim\text{Beta}\left(sq_j, s(1-q_j)\right).
\end{align}
In the hierarchical model, we fix sufficiently small $\tau_0$
$(1\gg\tau_0>0)$ so that  $(\beta_j, \gamma_j)$ has its probability mass 
concentrated around zero. Therefore, this represents the spike component of our prior specification. 
For the slab component, we consider $\tau_1$ to be large so that $\tau_1\ge 1$. This allows the prior for $(\beta_j,\gamma_j)$ to be flat beyond the spike component at the origin. 
We illustrate the components of a bivariate spike and slab prior in 
\cref{fig:ssbl} (with fixed $\sigma=1$). We generate the spike component 
with $\tau_0=0.001$ and the slab component with $\tau_1=5$.

@@

For the precision term $1/\sigma^2$, a natural choice of prior is the gamma distribution
as it allows the control of both the location and the scale of the precision.
%%% MT to TB: why not simply say the prior is exponential?
To ensure that the prior is able to represent the data, we consider $b=1$ and 
fix $a$ so that it represents the prior mean of the precision.
%%% MT to TB: "no prior information" seems a bit misleading here? I suggest removing
% In cases where we have no prior information,
We can simply consider a large enough value for $a$
%%% MT to TB: the next phrase is confusing... do you mean to say "with probability ..." (not sure what that is for [0,2a], but true value has probability of about 95% to be contained in [0,3a] for the exponential since 1-exp(-3) is about 95%))
so that the interval
$[0, 2a]$ contains the true value of the precision.
We use a beta prior to
model our uncertainty about
the selection probabilities $\pi_j$ where  $q_j$ represents our prior expectation of the selection probability ($\pi_j$) and $s$ acts as 
a concentration parameter.
For the causal effect, we want to use a Gaussian distribution that 
matches the scale of the noise term. Therefore, we consider $\beta_T\sim \normal(0,\sigma^2)$.
